---
title: "Activity #2: Applying Linear Regression Algorithms"
author: 
  - "Abigail Weinstein"
  - "Jeremy Ijoma"
  - "Max Krier"
date: 03-08-2026
format: 
    pdf:
      code-overflow: wrap
---

# I. Introduction

Per the activity description:

> "You and your team have been hired by the Nittany Valley Insurance Company to provide insight into how much an arbitrary health insurance policy might cost the company... Your goal is to build a predictive model for the charges based upon the available data using algorithms associated with linear regression."

The intention of this project is to develop an ideal predictive model of insurance claims costs for the Nittany Valley Insurance Company using strategies we have learned in class. The primary focus in this task is to evaluate the models using measures such as $R^2$, $RMSE$, $AIC$, etc. while building them using model selection algorithms and formulas (i.e., LASSO Regression, Backward Selection, etc.). It is also necessary for us as a team to evaluate the validity of these models, asking the question "is this model logical and realistic?". In doing this, we hope to have successfully created a predictive model that addresses the need for claims cost calculations effectively.

# II. Data Exploration

```{r}
#| results: "hide"
#| label: "data-preparation"
#| message: false
#| echo: false

#import libraries
library(readr)
library(dplyr)
library(ggplot2)
library(psych)
library(scales)
library(modelr)
library(glmnet)
library(ggpubr)
library(kableExtra)
library(knitr)

#load data
insurance_data_s26 <- read_csv("insurance_data_S26.csv")
insurance_validation <- read_csv("insurance_data_validation_S26.csv")
```

Prior to model building, it is necessary to understand the data we are working with. The activity instructions provided the following list of attribute descriptions. Attribute titles and data types incorporated in the list are our own additions, obtained through the `names` and `str` functions in $R$.

```{r}
#| label: "data-exploration-1"
#| results: "hide"
#| echo: false
insurance_data_s26 <- insurance_data_s26 %>% select(-c(`...1`))

names(insurance_data_s26)
str(insurance_data_s26)
summary(insurance_data_s26)
```
The data represents the range of  

> -   `age` : the age of the primary beneficiary (in years); numeric
> -   `sex` : the sex of the primary beneficiary; character
> -   `bmi`: the body mass index of the primary beneficiary $kg/m^2$; numeric
> -   `children`: the number of children/dependents of the primary beneficiary; numeric
> -   `smoker`: whether the primary beneficiary is a smoker; character
> -   `region`: which of four US geographical regions the primary beneficiary lives in; character
> -   `month`: the month in which the claim occurred; numeric
> -   `priorclaims`: the number of claims made by the primary beneficiary in the prior fiscal year; numeric
> -   **\*\*\*`charges`: the total charges billed to the policy (in US dollars); numeric\*\*\***

Using this list, we can make some assumptions about what we believe would produce the best predictive model. It will also help inform our interpretations of the models produced later on. It should be noted that there are multiple character-based attributes within this data. These attributes should be transformed to be dummies for the categories they represent. In addition to this, we also need to ensure that missing values are removed from the data. After this is completed, we can look at the size of our data set and begin examining initial relationships and distributions.

### Data Cleaning

```{r}
#| label: "data-cleaning"
#| results: "hide"
#| echo: false

#evaluate missingness + check dimensions
dim(insurance_data_s26)
insurance_data_s26_clean <- insurance_data_s26 %>% filter(!is.na(charges))
dim(insurance_data_s26_clean)

#transform dummies
insurance_data_s26_clean <- insurance_data_s26_clean %>% mutate(
  male = ifelse(sex == "male", 1, 0), 
  smoker = ifelse(smoker == "no", 0, 1)
) %>% select(-c(sex))
```

To clean the data, we first addressed the missing values. We did so by identifying the observations of the *outcome variable* and dropping them from the data set. There was only one such observation flagged, bring the count of observations from $861$ to $860$ in total. After addressing this concern, we then transformed some of our categorical variables to be numeric. The `smoker` variable was altered such that an entry of $1$ is equivalent to the "yes" response that was provided initially. The `sex` attribute was dropped in favor of the `male` attribute, which encodes those that were noted as "male" in the former as a positive ($1$) observation in the latter. We opted to leave region as it was, as altering encoding and making dummy variables is less intuitive than it is in its original form.

### Data Summary

With this, we can now examine the actual numeric elements of our data. This includes an exploration of summary statistics, outcome variable distribution, and cursory overview of attribute relationships.

```{r}
#| label: "tbl-data-summary"
#| echo: false

#needs formated!!!
tbl <- describe(insurance_data_s26_clean)
tbl <- tbl %>% select(c(n, min, median, mean, max, sd)) %>% filter(rownames(tbl) != "region*" & rownames(tbl) != "caseID")
tbl <- tbl %>% slice(5, 1:4, 6:10)
tbl <- kable(tbl, col.names = 
            c("", "Count", "Minimum", "Median", "Mean", "Maximum", "Std. Dev."),
            digits = 3, 
            format.args = list(big.mark = ",")) %>% row_spec(1, bold = TRUE) %>%
  kable_classic() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 
tbl

##BoxPlot display the statistics
ggplot(insurance_data_s26_clean, aes(x = as.factor(smoker), y = charges, fill = as.factor(smoker))) +
  geom_boxplot() +
  scale_x_discrete(labels = c("Non-Smoker", "Smoker")) +
  scale_fill_manual(values = c("lightgrey", "orange"), guide = "none") +
  labs(title = "Cost Difference by Smoking Status", x = "Smoker Status", y = "Charges ($)") +
  theme_classic()

```


In @tbl-data-summary, we can see the summary statistics for all variables in the data (with the exception of `region`). \[...\]
the summary statistics in the beneficiary population, the table show the average age (mean/median) of 39 ranging from 18 to 64 and number of children in beneficiary ranges from 0 to 5. BMI's mean/median is at 30.6. Though the mean and median are close in these variables, they seem to differ in insurance charges from 9,447 as the median and 13196 as the mean proving a right skewed scatterplot. This shows that a small statistical imbalance of the costs seem to impact the average greater.

the summary statistics in the beneficiary population, the table show the average age (mean/median) of 39 ranging from 18 to 64 and number of children in beneficiary ranges from 0 to 5. BMI's mean/median is at 30.6. Though the mean and median are close in these variables, they seem to differ in insurance charges from 9,447 as the median and 13196 as the mean proving a right skewed scatterplot. This shows that a small statistical imbalance of the costs seem to impact the average greater.

```{r}
#| label: "fig-data-dispersion"
#| echo: false
#| fig-cap: "Distribution of Claim Costs"

dens <- ggplot(insurance_data_s26_clean, aes(charges)) + geom_density(color = "red", linewidth = 1.25, fill = "red", alpha = .25) + labs(
  x = "Claims Costs (in USD)", 
  y = "Density", 
) + theme_minimal() + scale_y_continuous(labels = comma) + scale_x_continuous(labels = comma)

dens <- annotate_figure(dens, top = text_grob("Claims Costs (in USD) Distribution"))
dens

```

In @fig-data-dispersion, we see the distribution of the outcome variable, `charges`, in the form of a density plot. This density plot indicates to us that our outcome variable is *not* normally distributed, but rather right skewed. This aligns with the information presented in @tbl-data-summary. It is to be expected, of course, as there is a limit to how little something can cost but no cap for how much. This type of distribution is commonly seen in monetary distributions. What does this mean for our models though? It means that it will be difficult to accurately create a linear regression with this data, as the outcome variable itself is not normally distributed or linear in nature. To address this, we will transform the outcome variable by taking the natural log ($ln(x)$). This will allow us to more accurately predict the outcome variable using a linear model, as the outcome itself will now be linear. **From this point forward, the *logged* version of the outcome variable will be used.**

```{r}
#| label: "transform-outcome"
#| results: "hide"
#| echo: false

insurance_data_s26_clean <- insurance_data_s26_clean %>% mutate(
  log_charges = log(charges + 1)
)

```

### Exploring Relationships

Below are graphs showing a collection of a few of the relationships looked at in the project.  

```{r}
#| label: "BMI-Log-of-Claims-Smokers"
#| echo: false
#| fig-cap: "BMI Vs. Log of Claims Costs (In smokers)"

#Splitting the smokers from non-smokers to see if results change significantly
df <- split(insurance_data_s26_clean, insurance_data_s26_clean$smoker)
df_smoker <- df$yes
df_nonsmoker <- df$no

smoker_BMI_LogCharges <- ggplot(df_smoker, mapping = aes(log_charges, bmi)) + 
  geom_point(color = "black", alpha = 0.5, fill = "red", shape = 21, size = 2, stroke = 0.5) +
  geom_smooth(method = "lm", color = "red", linewidth = 1.25, alpha = 0.25) +
  labs(
    x = "Log of Claims Costs (in USD)", 
    y = "BMI", 
  ) + stat_poly_eq(use_label(c("eq", "R2")), formula = y ~ x, parse = TRUE) + 
  theme_minimal()
smoker_BMI_LogCharges <- annotate_figure(smoker_BMI_LogCharges, top = text_grob("BMI Vs. Log of Claims Costs (In smokers)"))
smoker_BMI_LogCharges
```

In the above figure, @BMI-Log-of-Claims, we see the relationship between the explanatory variable, `bmi`, and the response variable, `log_charges`, for only the smokers (those denoted with "yes" or 1 in the cleaned data).  The distribution shows a positive linear relationship.  The $R^2$ of the regression line is 0.62.  Thus, bmi explains 62% of the variation in the $log(charges)$ for smokers.  

```{r}
#| label: "BMI-Log-of-Claims-Non-Smokers"
#| echo: false
#| fig-cap: "BMI Vs. Log of Claims Costs (In non smokers)"

#Splitting the smokers from non-smokers to see if results change significantly
df <- split(insurance_data_s26_clean, insurance_data_s26_clean$smoker)
df_smoker <- df$yes
df_nonsmoker <- df$no

nonsmoker_BMI_LogCharges <- ggplot(df_nonsmoker, mapping = aes(log_charges, bmi)) + 
  geom_point(color = "black", alpha = 0.5, fill = "red", shape = 21, size = 2, stroke = 0.5) +
  geom_smooth(method = "lm", color = "red", linewidth = 1.25) +
  labs(
    x = "Log of Claims Costs (in USD)", 
    y = "BMI", 
  ) + stat_poly_eq(use_label(c("eq", "R2")), formula = y ~ x, parse = TRUE) + 
  theme_minimal()
nonsmoker_BMI_LogCharges <- annotate_figure(nonsmoker_BMI_LogCharges, top = text_grob("BMI Vs. Log of Claims Costs (In non smokers)"))
nonsmoker_BMI_LogCharges
```
In the above figure, @BMI-Log-of-Claims-Non-Smokers, we once again see the relationship between the explanatory variable, `bmi`, and the response variable, `log_charges`, for only the non smokers (those denoted with "no" or 0 in the cleaned data).  This distribution has a very flat non-linear distribution.  The relationship has a $R^2$ value of ~ 0, which gives very little confidence that bmi has any effect on charges of those that are not smokers.  

\[...\]

# III. Modeling 

Now we are ready to start building our models. As a team, we have decided to use the following model selection strategies to create our two primary models of interest: Step-wise Selection and LASSO Regression. Within these selection algorithms, we will be using the $AIC$ and 1-SE $MSE$ strategies respectively. As always, it is important to remember to split data as to not over fit the models. To evaluate our models, we will be using $RMSE$ and $R^2$.

```{r}
#| label: "data-split"
#| results: "hide"
#| echo: false

set.seed(12345) #set seed
train_index <- sample(
  x = 1:nrow(insurance_data_s26_clean), 
  size = floor(0.8*nrow(insurance_data_s26_clean))) 

#training and validation sets
insurance_train <- insurance_data_s26_clean[train_index, ]
insurance_test <- insurance_data_s26_clean[-train_index, ]

#sub-split for LASSO
insurance_train_input <- model.matrix(log_charges ~ . -caseID -charges, data = insurance_train)
insurance_train_output <- insurance_train$log_charges

insurance_test_input <- model.matrix(log_charges ~ . -caseID -charges, data = insurance_test )
insurance_test_output <- insurance_test$log_charges

```

To split the data, we will be using an $80/20$ random split such that $80$% of the data is in our training data and the other $20$% is in the testing/validation data. It is also necessary to create sub-splits of these sets for the LASSO regression. In this section and the next, you will see we omit the `caseID` and `charges` attributes. This is because they are either irrelevant to the model (`caseID`) or are a variation on our dependent variable. Including these will disturb the model, so it is necessary to remove them prior to creation.

### Model 1: Step-Wise Selection (AIC)

After using the step-wise selection algorithm on our testing data, we identified the model with the lowest $AIC$ (Akaike Information Criterion) out of all possible models. The resulting model included the following variables: `smoker`, `age`, `children`, `priorclaims`, `region`, `bmi`, and `male` (our modified version of `sex`). Below is the full model:

$$ \ln(charges) = 7.211 + 1.510X_{smoker,i} + 0.034X_{age, i} + 0.091X_{children, i} $$
$$ -0.058X_{priorclaims, i} - 0.108X_{regionNW, i} - 0.228X_{regionSE, i} - 0.206X_{regionSW, i} + 0.014X_{bmi, i} - 0.071X_{male, i} $$

The first item that should be noted is that the outcome variable is represented as a natural log here. This influences how all other coefficients are interpreted. Instead of each coefficient-attribute pair contributing $x$ dollars to the total value of claims costs, it represents the contribution to the logged value of those costs. As such, the each coefficient does not represent an increase of $\beta$ per unit (as in summation), but rather the product of $e^{\beta * X}$ **in relation to the outcome as it is in US dollars**. For instance, for every unit increase in `age`, for example, the natural log of `charges` will increase by $0.034$, which translates to it being multiplied by a factor of $e^{.034X}$. For most of the attributes in this model, it is simply a matter of whether or not it occurs, as they are dichotomous categorical variables. If an insurance claim is made by a man, for example, the cost to the insurance company decreases by $.07$ logged USD *or* by a factor of $1.07$ when extrapolating the formula to the un-transformed dollar. While it does become more complicated, this transformation allows us to have what really should be a logarithmic regression in the form of a linear one.

Beyond this aspect of the model, we should also note that the *northeastern* class of `region` is being used as the baseline region in this model. For every other region, claims cost decrease from this baseline. Other factors that contribute to *lower* claims costs for the insurance company, according to this model, include number of prior claims and individual has made and if the individual filing that claim is a man. Factors that increase claims costs are claimant BMI, age, and smoking. The baseline (intercept) of this model translates to approximately $1,354$ USD. It should be noted that this value is the cost to the company assuming that claimant is a female infant, which is unrealistic both in reality and in this data, as it only includes adults.

Finally, it should be noted that all of these attributes have a relatively small effect on claim costs compared to that of our `smoking` attribute. Of course, `age` and `bmi` are continuous and begin at greater values (see @tbl-data-summary), so they become scaled to a greater effect within the model. As such, we could argue that the most influential attributes, according to this model are `age`, `bmi`, and `smoker`.

```{r}
#| label: "model-sws-aic"
#| results: "hide"
#| message: false
#| echo: false
#prep models
nullModel <- lm(log_charges ~ 1, data = insurance_train)
fullModel <- lm(log_charges ~ . -caseID -charges, data = insurance_train)

#final model build
model1 <- step(
  object = nullModel, 
  scope = list(
    lower = nullModel, 
    upper = fullModel
  ), 
  data = insurance_train, 
  direction = "both",
  k = 2, 
  trace = 0
)

summary(model1)

```

### Model 2: LASSO Regression (1-SE MSE)

Our second model we created using the LASSO regression method, which scales coefficients to zero relative to least-squares estimates. We identify this scaling factor ($\lambda$) by identifying the point at which the lowest mean-squared error ($MSE$) exists and identifying from there the simplest model within one standard error of that point. Those values themselves are determined through cross-validation processes. In this instance the resulting model contains the following four attributes: `age`, `children`, `smoker`, and `priorclaims`. The full model is below:

$$
\ln(charges) = 7.581 + 0.031X_{age, i} + 0.053X_{children, i} + 1.341X_{smoker, i} - 0.014X_{priorclaims, i}
$$

Like Model 1, this model is also in terms of the natural log of `charges`. This means that, when computing the costs in raw USD, it is not adding $\beta X$ to the intercept, but multiplying that intercept by $e^{\beta X}$. This model, as is common in uses of LASSO regression, contains very few attributes. Of these attributes, all were included in our previous model. Relationships between `charges` and the attributes themselves remain the same; a claimant's age, smoking status, and number of children all increase costs to the insurance company. Prior claims made by that claimant decrease costs. What is different, though, is the scale of impact. Rather than coefficients increasing, as one would presume when parameters a decreased but the same outcomes are desired, they *decrease*. Smoking now only increase logged costs by $1.341$ USD rather than $1.51$. While this is a small change in logged terms, it becomes more substantial after data is transformed back to its original form.

The transfer of influence on the outcome is then transferred from these attributes to the intercept itself, which is valued at a scaled $1,960$ USD. Again, it should be noted this is assuming infancy. Were we to set the baseline of age in this regression at the point it is in the raw data ($18$ years of age), this value would be closer to $3,424$ USD. It is extremely interesting that this shift occurred within the model while excluding one of the other heavy-hitting attributes from the previous model (`bmi`).

```{r}
#| label: "model-lasso"
#| results: "hide"
#| message: false
#| echo: false

#set seed
set.seed(54321)

#build model
model2 <- cv.glmnet(
  x = insurance_train_input, 
  y = insurance_train_output, 
  family = "gaussian", 
  alpha = 1, 
  lambda = NULL, 
  standardize = TRUE, 
  nfolds = 10
)

model_2 <- predict(model2, s = model2$lambda.1se, type = "coefficients")
model_2 <- data.frame(name = model_2@Dimnames[[1]][model_2@i + 1], coefficient = model_2@x)
model_2

```

# V. Results

Now that we have our models and an understanding of what they mean, it is important that we validate each of them. Validation will first be conducted with respect to the *testing* sets constructed earlier in this report. As mentioned earlier, we are to be utilizing the $RMSE$ and $R^2$ to evaluate each of these models. In addition, we have been provided with another unique data set for the models to be assessed on. Each model will then have interpretations provided for results of both cross-validation assessments and the unseen data assessments. This, of course, is in addition to the contextual interpretations of the models provided earlier. After this, we will select the model we believe to be the best.

As a refresher, these are the formulas for both $RMSE$ and $R^2$:

$$
RMSE = 1 - ( \sum(\hat{y_i} - y_i)^2 / \sum(y_i- \bar{y})^2)
$$

$$
R^2 = \sqrt{1/n * (y_i - \hat{y_i})^2}
$$

$RMSE$ evaluates the average error (in units of the outcome) from the true value of the observation and is used as a measure of accuracy. $R^2$ evaluates the proprotion of total variance accounted for within the model and is often used as a measure of fit.

### Model 1 Cross Validation

```{r}
#| label: "model-1-validation"
#| results: "hide"
#| echo: false

#predict values
model1_predicted <- predict(model1, newdata = insurance_test)

#calculate R^2
rss <- sum((model1_predicted - insurance_test_output)^2)  
tss <- sum((insurance_test_output - mean(insurance_test_output))^2)
r2 <- 1- (rss/tss)
r2
#calculate RMSE
mse <- modelr::mse(model = model1, data = insurance_test)
rmse <- sqrt(mse)
rmse

rmse_factor <- exp(rmse)
rmse_factor
```

The reported statistics for Model 1, the step-wise selection model determined using AIC, are as follows:

$$
R^2: .7694
$$

$$
RMSE: .4781
$$

The $R^2$ indicates to us that approximately $77$% of variation in the data evaluated is accounted for by the model. The closer to $100$% this value is, the better fit your model for that particular set of data. We evaluate the $R^2$ on the testing set so that we can determine whether or not our data has been overfit to the training set. In this instance, this model actually performed better on the testing data than on the training data ($R^2 = .75$).

The $RMSE$ of this model is misleading. $RMSE$ is in the unit of measure that the outcome variable is in. In this instance, it is logged USD. Because we are working with logged data, this seemingly small value of $.4781$ carries a bit more weight. In the raw version of our `charges` variable, this $RMSE$ translates to an error factor of $1.61$, meaning that the true value of our observations is on average within \[$\hat{y_i}/1.61, \hat{y_i} *1.61$\] of our predicted value.

### Model 2 Cross Validation

```{r}
#| label: "model-2-validation"
#| results: "hide"
#| echo: false

#predict values
model2_predicted <- predict(model2, s = model2$lambda.1se, newx = insurance_test_input)

#calculate R^2
rss <- sum((model2_predicted - insurance_test_output)^2)  
tss <- sum((insurance_test_output - mean(insurance_test_output))^2)
r2 <- 1- (rss/tss)
r2
#calculate RMSE
rmse <- sqrt(mean((insurance_test_output - model2_predicted)^2))
rmse

rmse_factor <- exp(rmse)
rmse_factor
```

The reported statistics for Model 1, the step-wise selection model determined using AIC, are as follows:

$$ R^2: .7328 $$

$$ RMSE: .5146 $$

The $R^2$ for Model 2 is $.7328$, indicating that approximately $73$% of the variation within the data is accounted for by the model. This is slightly lower than our previous models fit, but not by much. The $RMSE$, sitting at $.5146$. This translates to an error factor of $1.67$. This value tells us that the true logged cost to the insurance company is on average $.5146$ units away from the predicted logged cost. This translates to an an error rate of \~ $67$% in either direction when taken at the raw dollar value.

### Final Test Validation

Before we can use the validation data provided to us, we need to transform the `sex`, `smoker`, and `charges` elements. This is because these attributes were manipulated during model creation. For validation to be effective, the data must align with the model structure. As such, we transform `sex` and `smoker` attributes into dummy variables and take the natural log of the `charges` outcome attribute. It is also necessary to split into input and output groups for easier calculations later on.

```{r}
#| label: "validation-set-clean"
#| results: "hide"
#| echo: false

insurance_validation <- insurance_validation %>% filter(!is.na(charges)) %>% select(-c(`...1`))
dim(insurance_validation)

#transform dummies
insurance_validation <- insurance_validation %>% mutate(
  male = ifelse(sex == "male", 1, 0), 
  smoker = ifelse(smoker == "no", 0, 1)
) %>% select(-c(sex))


#transform outcome
insurance_validation <- insurance_validation %>% mutate(
  log_charges = log(charges + 1)
)

#split data input/output
insurance_validation_input <- model.matrix(log_charges ~ . -charges -caseID, data = insurance_validation)
insurance_validation_output <- insurance_validation$log_charges
```

```{r}
#| label: "validation-set-test"
#| results: "hide"
#| echo: false

#model 1 test
model1_predicted <- predict(model1, newdata = insurance_validation)
rmse1 <- sqrt(mean((insurance_validation_output - model1_predicted)^2))
rmse1
rmse1_factor <- exp(rmse1)
rmse1_factor

#model 2 test
model2_predicted <- predict(model2, s = model2$lambda.1se, newx = insurance_validation_input)
rmse2 <- sqrt(mean((insurance_validation_output - model2_predicted)^2))
rmse2
rmse2_factor <- exp(rmse2)
rmse2_factor
```

The final test for these models are to evaluate them on completely unseen data. Evaluations are being conducted through *only* $RMSE$. The resulting $RMSE$ values are as follows:

$$
RMSE_{M1} = .4145
$$

$$
RMSE_{M2} = .4289
$$

While they are very close, our first model indicates less deviation from both logged and true values of the outcome variable ($.4145 < .4289$). With this information from unseen, unrelated data and the outcomes from our previous validation measures, we argue that the best model to use out of those presented here is **Model 1**.

### The Final Model: Step-Wise Selection w/ AIC

The final model recommended for Nittany Valley Insurance Company is **Model 1: Step-Wise Selection w/ AIC**. This model incorporates a number of attributes from the data provided (`smoker`, `age`, `children`, `priorclaims`, `region`, `bmi`, and `sex`) to create a model that is fairly well fit and does not deviate too strongly from true values in both the logged data used to create the models and the raw data that the models will be applied to. The model, shown below, addresses the three "big" factors that are commonly agreed upon to have substantial influence on claims costs and provides evidence to support that belief.

$$ \ln(charges) = 7.211 + 1.510X_{smoker,i} + 0.034X_{age, i} + 0.091X_{children, i} $$
$$ -0.058X_{priorclaims, i} - 0.108X_{regionNW, i} - 0.228X_{regionSE, i} - 0.206X_{regionSW, i} + 0.014X_{bmi, i} - 0.071X_{male, i} $$

# V. Final Recommendations

While the authors used the a logarithmic transformation to address normality concerns such that a linear model would be more accurate, it should be noted that this transformation does not ensure normality. A closer look at the data will reveal an uneven, albeit more normal distribution of the outcome variable. It may be for this reason we saw larger $RMSE$s. We recommend that, in the future, a strictly non-linear approach is taken to predict costs to the company. These will likely be more accurate all around. It would still be recommended that factors such as age, BMI, smoking habits, and more are taken into consideration when creating those models.

For the team working on this report, we recognize that more validation measures and plots should be included in the future to help support the validity of those models. Examples include QQ-plots and residual plots.

# VI. Author Contributions
Jeremy:
- Setting up the github repository

Abigail:

Abigail Weinstein: All code. All inductory and explanatory text for Data Cleaning, Modeling, Results, and Final Recommendation. @tbl-data-summary and @fig-data-dispersion.

Jeremy Ijoma: Data summary interpretation, created GitHub repository, brainstorming.

Max Krier: Exploring relationships visuals and explanations, brainstorming

# VII. Code Appendix

```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```
