---
title: "Activity #2: Applying Linear Regression Algorithms"
author: 
  - "Abigail Weinstein"
  - "Jeremy Ijoma"
  - "Max Krier"
date: 03-08-2026
format: pdf
---

# I. Introduction

Per the activity description:

> "You and your team have been hired by the Nittany Valley Insurance Company to provide insight into how much an arbitrary health insurance policy might cost the company... Your goal is to build a predictive model for the charges based upon the available data using algorithms associated with linear regression."

The intention of this project is to develop an ideal predictive model of insurance claims costs for the Nittany Valley Insurance Company using strategies we have learned in class. The primary focus in this task is to evaluate the models using measures such as $R^2$, $RMSE$, $AIC$, etc. while building them using model selection algorithms and formulas (i.e., LASSO Regression, Backward Selection, etc.). It is also necessary for us as a team to evaluate the validity of these models, asking the question "is this model logical and realistic?". In doing this, we hope to have successfully created a predictive model that addresses the need for claims cost calculations effectively.

# II. Data Exploration

```{r}
#| results: "hide"
#| label: "data-preparation"
#| message: false
#| echo: false

#import libraries
library(readr)
library(dplyr)
library(ggplot2)
library(psych)
library(scales)
library(modelr)
library(glmnet)
library(ggpubr)
library(kableExtra)
library(knitr)

#load data
insurance_data_s26 <- read_csv("insurance_data_S26.csv")
insurance_valdiation <- read_csv("insurance_data_validation_S26.csv")
```

Prior to model building, it is necessary to understand the data we are working with. The activity instructions provided the following list of attribute descriptions. Attribute titles and data types incorporated in the list are our own additions, obtained through the `names` and `str` functions in $R$.

```{r}
#| label: "data-exploration-1"
#| results: "hide"
#| echo: false
insurance_data_s26 <- insurance_data_s26 %>% select(-c(`...1`))

names(insurance_data_s26)
str(insurance_data_s26)
summary(insurance_data_s26)
```
The data represents the range of  

> -   `age` : the age of the primary beneficiary (in years); numeric
> -   `sex` : the sex of the primary beneficiary; character
> -   `bmi`: the body mass index of the primary beneficiary $kg/m^2$; numeric
> -   `children`: the number of children/dependents of the primary beneficiary; numeric
> -   `smoker`: whether the primary beneficiary is a smoker; character
> -   `region`: which of four US geographical regions the primary beneficiary lives in; character
> -   `month`: the month in which the claim occurred; numeric
> -   `priorclaims`: the number of claims made by the primary beneficiary in the prior fiscal year; numeric
> -   **\*\*\*`charges`: the total charges billed to the policy (in US dollars); numeric\*\*\***

Using this list, we can make some assumptions about what we believe would produce the best predictive model. It will also help inform our interpretations of the models produced later on. It should be noted that there are multiple character-based attributes within this data. These attributes should be transformed to be dummies for the categories they represent. In addition to this, we also need to ensure that missing values are removed from the data. After this is completed, we can look at the size of our data set and begin examining initial relationships and distributions.

### Data Cleaning

```{r}
#| label: "data-cleaning"
#| results: "hide"
#| echo: false

#evaluate missingness + check dimensions
dim(insurance_data_s26)
insurance_data_s26_clean <- insurance_data_s26 %>% filter(!is.na(charges))
dim(insurance_data_s26_clean)

#transform dummies
insurance_data_s26_clean <- insurance_data_s26_clean %>% mutate(
  male = ifelse(sex == "male", 1, 0), 
  smoker = ifelse(smoker == "no", 0, 1)
) %>% select(-c(sex))
```

To clean the data, we first addressed the missing values. We did so by identifying the observations of the *outcome variable* and dropping them from the data set. There was only one such observation flagged, bring the count of observations from $861$ to $860$ in total. After addressing this concern, we then transformed some of our categorical variables to be numeric. The `smoker` variable was altered such that an entry of $1$ is equivalent to the "yes" response that was provided initially. The `sex` attribute was dropped in favor of the `male` attribute, which encodes those that were noted as "male" in the former as a positive ($1$) observation in the latter. We opted to leave region as it was, as altering encoding and making dummy variables is less intuitive than it is in its original form.

### Data Summary

With this, we can now examine the actual numeric elements of our data. This includes an exploration of summary statistics, outcome variable distribution, and cursory overview of attribute relationships.

```{r}
#| label: "tbl-data-summary"
#| echo: false

#needs formated!!!
tbl <- describe(insurance_data_s26_clean)
tbl <- tbl %>% select(c(n, min, median, mean, max, sd)) %>% filter(rownames(tbl) != "region*" & rownames(tbl) != "caseID")
tbl <- tbl %>% slice(5, 1:4, 6:10)
tbl <- kable(tbl, col.names = 
            c("", "Count", "Minimum", "Median", "Mean", "Maximum", "Std. Dev."),
            digits = 3, 
            format.args = list(big.mark = ",")) %>% row_spec(1, bold = TRUE) %>%
  kable_classic() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 
tbl
```

In @tbl-data-summary, we can see the summary statistics for all variables in the data (with the exception of `region`). \[...\]

```{r}
#| label: "fig-data-dispersion"
#| echo: false
#| fig-cap: "Distribution of Claim Costs"

dens <- ggplot(insurance_data_s26_clean, aes(charges)) + geom_density(color = "red", linewidth = 1.25, fill = "red", alpha = .25) + labs(
  x = "Claims Costs (in USD)", 
  y = "Density", 
) + theme_minimal() + scale_y_continuous(labels = comma) + scale_x_continuous(labels = comma)

dens <- annotate_figure(dens, top = text_grob("Claims Costs (in USD) Distribution"))
dens

```

In @fig-data-dispersion, we see the distribution of the outcome variable, `charges`, in the form of a density plot. This density plot indicates to us that our outcome variable is *not* normally distributed, but rather right skewed. This aligns with the information presented in @tbl-data-summary. It is to be expected, of course, as there is a limit to how little something can cost but no cap for how much. This type of distribution is commonly seen in monetary distributions. What does this mean for our models though? It means that it will be difficult to accurately create a linear regression with this data, as the outcome variable itself is not normally distributed or linear in nature. To address this, we will transform the outcome variable by taking the natural log ($ln(x)$). This will allow us to more accurately predict the outcome variable using a linear model, as the outcome itself will now be linear. **From this point forward, the *logged* version of the outcome variable will be used.**

```{r}
#| label: "transform-outcome"
#| results: "hide"
#| echo: false

insurance_data_s26_clean <- insurance_data_s26_clean %>% mutate(
  log_charges = log(charges + 1)
)

```

### Exploring Relationships

\[...\]

# III. Modeling 

Now we are ready to start building our models. As a team, we have decided to use the following model selection strategies to create our two primary models of interest: Step-wise Selection and LASSO Regression. Within these selection algorithms, we will be using the $AIC$ and 1-SE $MSE$ strategies respectively. As always, it is important to remember to split data as to not over fit the models. To evaluate our models, we will be using $RMSE$ and $R^2$.

```{r}
#| label: "data-split"
#| results: "hide"
#| echo: false

set.seed(12345) #set seed
train_index <- sample(
  x = 1:nrow(insurance_data_s26_clean), 
  size = floor(0.8*nrow(insurance_data_s26_clean))) 

#training and validation sets
insurance_train <- insurance_data_s26_clean[train_index, ]
insurance_test <- insurance_data_s26_clean[-train_index, ]

#sub-split for LASSO
insurance_train_input <- model.matrix(log_charges ~ . -caseID -charges, data = insurance_train)
insurance_train_output <- insurance_train$log_charges

insurance_test_input <- model.matrix(log_charges ~ . -caseID -charges, data = insurance_test )
insurance_test_output <- insurance_test$log_charges

```

To split the data, we will be using an $80/20$ random split such that $80$% of the data is in our training data and the other $20$% is in the testing/validation data. It is also necessary to create sub-splits of these sets for the LASSO regression. In this section and the next, you will see we omit the `caseID` and `charges` attributes. This is because they are either irrelevant to the model (`caseID`) or are a variation on our dependent variable. Including these will disturb the model, so it is necessary to remove them prior to creation.

### Model 1: Step-Wise Selection (AIC)

After using the step-wise selection algorithm on our testing data, we identified the model with the lowest $AIC$ out of all possible models. The resulting model included the following variables: `smoker`, `age`, `children`, `priorclaims`, `region`, `bmi`, and `male` (our modified version of `sex`). Below is the full model:

$$ \ln(charges) = 7.211 + 1.510X_{smoker,i} + 0.034X_{age, i} + 0.091X_{children, i} $$
$$ -0.058X_{priorclaims, i} - 0.108X_{regionNW, i} - 0.228X_{regionSE, i} - 0.206X_{regionSW, i} + 0.014X_{bmi, i} - 0.071X_{male, i} $$

\[interpretation\]
This model from the Step-Wise regression techniques uses age, smoking status, and BMI to show the primary causes of insurance costs. This is shown through Adjusted R-squared. It seems to show smoking status as the largest relative impact.

```{r}
#| label: "model-sws-aic"
#| results: "hide"
#| message: false
#| echo: false
#prep models
nullModel <- lm(log_charges ~ 1, data = insurance_train)
fullModel <- lm(log_charges ~ . -caseID -charges, data = insurance_train)

#final model build
model1 <- step(
  object = nullModel, 
  scope = list(
    lower = nullModel, 
    upper = fullModel
  ), 
  data = insurance_train, 
  direction = "both",
  k = 2, 
  trace = 0
)

summary(model1)

```

### Model 2: LASSO Regression (1-SE MSE)

Our second model we created using the LASSO regression method, which scales coefficients to zero relative to least-squares estimates. We identify this scaling factor ($\lambda$) by identifying the point at which the lowest mean-squared error ($MSE$) exists and identifying from there the simplest model within one standard error of that point. Those values themselves are determined through cross-validation processes. In this instance the resulting model contains the following four attributes: `age`, `children`, `smoker`, and `priorclaims`. The full model is below:

$$
\ln(charges) = 7.581 + 0.031X_{age, i} + 0.053X_{children, i} + 1.341X_{smoker, i} - 0.014X_{priorclaims, i}
$$

\[interpretation\]
Through LASSO Regression, the model shows singular influence of insurance risk. One Standard Error selects the one model that is simplified and minimized but can still perform within a good margin of the result.
```{r}
#| label: "model-lasso"
#| results: "hide"
#| message: false
#| echo: false

#set seed
set.seed(54321)

#build model
model2 <- cv.glmnet(
  x = insurance_train_input, 
  y = insurance_train_output, 
  family = "gaussian", 
  alpha = 1, 
  lambda = NULL, 
  standardize = TRUE, 
  nfolds = 10
)

model2 <- predict(model2, s = model2$lambda.1se, type = "coefficients")
model2 <- data.frame(name = model2@Dimnames[[1]][model2@i + 1], coefficient = model2@x)
model2

```

# V. Results

Now that we have our models and an understanding of what they mean, it is important that we validate each of them. As mentioned earlier, we are to be utilizing the $RMSE$ and $R^2$ to evaluate each of these models. In addition, we have been provided with another unique data set for the models to be assessed on. Each model will then have interpretations provided for results of both cross-validation assessments and the unseen data assessments. This, of course, is in addition to the contextual interpretations of the models. After this, we will select the model we believe to be the best.

### Model 1 Cross Validation

```{r}
#| label: "model-1-validation"
#| results: "hide"
#| echo: false

#predict values
model1_predicted <- predict(model1, newx = insurance_test)

#calculate R^2
r_squared_value <- summary(model1)$r.squared

print(r_squared_value)

#calculate RMSE

mse_value <- mean(residuals(model1))
rmse_value <- mse_value^2

print(mse_value)
print(rmse_value)
```

### Model 2 Cross Validation

### Final Test Validation

Before we can use the validation data provided to us, we need to transform the `sex`, `smoker`, and `charges` elements. This is because these attributes were manipulated during model creation. For validation to be effective, the data must align with the model structure. As such, we transform `sex` and `smoker` attributes into dummy variables and take the natural log of the `charges` outcome attribute.

```{r}
#| label: "validation-set-clean"
#| results: "hide"
#| echo: false

insurance_valdiation <- insurance_valdiation %>% filter(!is.na(charges))
dim(insurance_valdiation)

#transform dummies
insurance_valdiation <- insurance_valdiation %>% mutate(
  male = ifelse(sex == "male", 1, 0), 
  smoker = ifelse(smoker == "no", 0, 1)
) %>% select(-c(sex))


#transform outcome
insurance_valdiation <- insurance_valdiation %>% mutate(
  log_charges = log(charges + 1)
)
```

### The Final Model: ...

# V. Final Recommendations

# VI. Author Contributions
Jeremy:
- Setting up the github repository

Abigail:

Max:
# VII. Code Appendix

```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```
